FictionEro - Affective Impact of Fiction

### 2024-12-09 study1/analysis/2_emotions.qmd
push
formatting

This section is about selecting the best model and making a **manipulation check** to make sure that the emotional appraisal were sensitive to the main manipualtion (Neutral vs. Emotional).

@@

>>>>

This section is about selecting the best model and making a **manipulation check** to make sure that the emotional appraisal were sensitive to the main manipulation (Neutral vs. Emotional).

@@

<!-- Effect becomes larger, more significant and goes in both directions for both genders -->
